Modelling the Retinotectal projection - can competition provide a stopping mechanism?

### 2021-09-10 paper/paper.tex
Add division by |B| to I and J

>>>>

\subsection*{Observations/Notes}

J has a repulsive effect, which is generally disordering. If competition has
`a lot of work to do' (i.e. in the m\_ee... models) then a strong J will push
the axons across the whole tissue, but will upset the local ordering
relationships. Perhaps J also needs a self-self interaction (i.e. for members
of the same axon?).
